### 2020-02-06 thesis/paper.tex
more using of tool

>>>>

In the top left the selector allows for choosing clustering algorithms to add to the workflow. When an algorithm is selected the corresponding options panel appears in the right allowing to define the parameter ranges that should be sampled. For each parameter the values used for clustering are drawn from a uniform distribution for each run, the number of runs can be defined in the ``Samples'' field. For some algorithms, where there is only the parameter for the number of clusters $k$ as for k-Means, the ``Samples Each'' setting defines how many runs to perform for each value within the range instead of the total number of samples. This is the case as for such methods randomly sampling $k$ is usually not desired, only running the algorithm multiple times for each $k$, as random factors may impact the result. When all parameter ranges and the number of samples are defined, the clustering task can be added to the workflow with the ``Confirm'' button in the bottom right. If a clustering task should be removed, the ``X'' button besides the task can be clicked.

For ease of use, workflows can be saved and loaded in the workflow-view, usind the ``Save Wf'' and ``Load Wf'' buttons respectively. The tool creates custom Clustering Workflow Files (CWF) for this, allowing to re-use and modify workflows throughout multiple executions of the tool.

In the bottom left, additional options are available, which are not saved in the CWF files as the user should should set them manually. Setting a seed other than $-1$ allows to seed the clustering algorithms such that re-running them produces the same result every time, making results reproducible. For meta-clustering the OPTICS \cite{10.1145/304181.304187} algorithm is used as it produces a useful reachability plot in the meta-view, allowing for the identification of dense result regions, possibly indicating robustness. The Epsilon and MinPTS parameters allow to define the settings for the OPTICS algorithm, making it possible to define how close clustering results must be to be considered reachable and how many points need to be in this range. With these options, the user is able to define how densely clustering results must occur for them to be shown as robust in the meta-view. The default parameters are chosen such that clusterings are always considered reachable and the neighborhood only considers the closest neighbor for reachability, leading to a DBSCAN-like result. To select the distance function used by OPTICS the selector in the bottom right, just above ``Execute Workflow'' can be used. The ``Execute Workflow'' button is available as soon as at least one clustering task is added.

The additional check boxes in the bottom right allow adding the ground truth to the meta-view (if available) and to manage trivial solutions. Trivial solutions are in this case the solutions in which either all points were clustered into one cluster or each point was assigned its own cluster. One can both delete trivial solutions occurring from the clustering algorithms and forcefully add them to the result. These solutions might prove useful when comparing the NMI value of other solutions to the ground truth, to gain an idea of how good the value is.

When all setting are defined, the user can press the ``Execute Workflow'' button, launching a task that runs the algorithms and opens the meta-view with the computed results. In this step the meta-clustering with OPTICS \cite{10.1145/304181.304187} is also performed.

If the user has a previously saved Clustering Result File (CRF), which can be created in the meta-view, he can also omit defining a workflow and load the results in through the ``Load Result'' button. This button is only available when no clustering tasks were added to the workflow. Before loading a result though, the user should make sure that the settings in the bottom left for meta-clustering are set to his liking. Only the seed field has no effect when loading a result as no clustering algorithms, except for meta-clustering which is deterministic, are run. After the data is loaded and meta-clustering is performed the meta-view opens with the chosen data.
